Analyzing Trends on the Characteristics of Notable People on Wikipedia

### 2024-12-14 paper/paper.qmd
updates paper by making some graphs fit on page, updates model

```{r}
#| label: fig-time_period_prediction
#| fig-cap: Model-Predicted Distributions of Percentile Rank by Time Period. Bars Shown On the Bottom Denote the Standard Deviation of the Prediction, With More Variability for Less Represented Time Periods (such as before 500 AD)
#| echo: false
#| warning: false

@@

ggplot(normal_distributions, aes(x = x, y = density, color = time_period, fill = time_period)) +
  geom_line(size = 1.2) +  # Density curve
  geom_area(alpha = 0.2, position = "identity") +  # Filled area
  geom_vline(aes(xintercept = mean), linetype = "solid", linewidth = 0.8) +  # Mean
  geom_errorbarh(aes(xmin = mean - 1.96 * sd, xmax = mean + 1.96 * sd, y = 0), 
                 height = 0.1, color = "black", linetype = "dashed") +  # Confidence intervals
  facet_wrap(~time_period, ncol = 1, scales = "free_y") +  # Vertical facets by time period
  theme_minimal() +
  scale_y_continuous( breaks = seq(0, 4, by = 2)) +
  labs(
    x = "Predicted Prominence Percentile",
    y = "Density"
  ) +
  theme(
    strip.text = element_text(size = 14),
    panel.spacing = unit(0.5, "lines")
  )
```

@fig-time_period_prediction highlights the large variation in model predictions based on the time period the individual was born in. Although those born in earlier time periods tend to have significantly higher prominence, there were also a much lower amount of them.

@@

\`\newpage

@@

```{r, fig.width=8, fig.height = 30}
#| label: tbl-full-modelsummary-results
#| tbl-cap: Full Results of the Model, Including Characteristics Not Strongly Associated With Wikipedia Prominence
#| echo: false
#| warning: false

@@

model_summary= modelsummary(BIC_model, output = "default")

model_summary
```

>>>>

```{r, out.width='70%', out.height='70%'}
#| label: fig-time_period_prediction
#| fig-cap: Model-Predicted Distributions of Percentile Rank by Time Period. Bars Shown On the Bottom Denote the Standard Deviation of the Prediction, With More Variability for Less Represented Time Periods (such as before 500 AD)
#| echo: false
#| warning: false

@@

ggplot(normal_distributions, aes(x = x, y = density, color = time_period, fill = time_period)) +
  geom_line(size = 1.2) +  # Density curve
  geom_area(alpha = 0.2, position = "identity") +  # Filled area
  geom_vline(aes(xintercept = mean), linetype = "solid", linewidth = 0.8) +  # Mean
  geom_errorbarh(aes(xmin = mean - 1.96 * sd, xmax = mean + 1.96 * sd, y = 0), 
                 height = 0.1, color = "black", linetype = "dashed") +  # Confidence intervals
  facet_wrap(~time_period, ncol = 1, scales = "free_y") +  # Vertical facets by time period
  theme_minimal() +
  scale_y_continuous( breaks = seq(0, 4, by = 2)) +
  labs(
    x = "Predicted Prominence Percentile",
    y = "Density"
  ) +
  theme(
    strip.text = element_text(size = 14),
    panel.spacing = unit(0.5, "lines")
  )
```
\newpage
@fig-time_period_prediction highlights the large variation in model predictions based on the time period the individual was born in. Although those born in earlier time periods tend to have significantly higher prominence, there were also a much lower amount of them.

@@

@@

```{r, tbl.width=1, tbl.height=5}
#| label: tbl-full-modelsummary-results
#| tbl-cap: Full Results of the Model, Including Characteristics Not Strongly Associated With Wikipedia Prominence
#| echo: false
#| warning: false

@@

# modelsummary(BIC_model, output = "default", table.font.size = 4)

modelsummary(BIC_model, output = "kableExtra", statistics = NULL) |>
    kable_styling(font_size = 8, full_width = FALSE, bootstrap_options = "striped", position = "center") |>
    row_spec(0, bold = TRUE)
```
